A Bioconductor Workflow for Processing and Analysing Spatial Proteomics Data

### 2016-06-14 bioc-workflow.Rmd
plot2D with other PCs

There are other dimensionality reduction methods available in the
`plot2D` function, which can be parametrised with the `method`
argument.

**TODO** Advantages, disadvantages? See
[this](https://gist.github.com/mikelove/74bbf5c41010ae1dc94281cface90d32)
very interesting gist with intriguing tSNE examples. This might be
better to come after markers.

@@

We now visualise these annotations along the PCA plot using the
`plot2D` function. We also use the `addLegend` function to map the
marker classes to the pre-defined colours.

```{r plotmarkers}
## Plot mouse markers
plot2D(hl, fcol = "markers", main = "pRolocmarkers for mouse")
addLegend(hl, fcol = "markers", where = "bottomleft", cex = .7)
```

@@

```{r}
data(hyperLOPIT2015ms3r1)
data(hyperLOPIT2015ms3r2)
data(hyperLOPIT2015ms3r3)

@@

ij <- combn(3, 2)
pc <- apply(ij, 2,
            function(.ij) {
                tmp <- suppressMessages(commonFeatureNames(hll[.ij]))
                diag(cor(t(exprs(tmp[[1]])), t(exprs(tmp[[2]]))))
            })
names(pc) <- apply(ij, 2, paste, collapse = ".")
sapply(pc, summary)
```

>>>>

**TODO** There are other dimensionality reduction methods available in
the `plot2D` function, which can be parametrised with the `method`
argument.  Advantages, disadvantages? See
[this](https://gist.github.com/mikelove/74bbf5c41010ae1dc94281cface90d32)
very interesting gist with intriguing tSNE examples. This might be
better to come after markers.

It is also useful to visualise the relative intensities along the
gradient to identify fractions displaying particularly low yield. This
can be done using the `plotDist` and `boxplot` functions, that plot
the protein profiles occupancy along the gradient (we also display the
mean fraction intensities) and a `boxplot` of the column
intensities. In the two plots displayed below, we re-order the
fractions to pair corresponding fractions in the two replicates
(rather than ordering the fractions by replicate).

```{r qcbx, fig.width = 12}
par(mfrow = c(1, 2))
o <- order(hyperLOPIT$Fraction.No)
plotDist(hyperLOPIT[, o], pcol = "#00000010")
lines(colMeans(exprs(hyperLOPIT[, o])), col = "red", type = "b")
boxplot(exprs(hyperLOPIT[, o]))
```

@@

We now visualise these annotations along the PCA plot using the
`plot2D` function. We also use the `addLegend` function to map the
marker classes to the pre-defined colours. We also display the data
along the first and seventh PCs using the `dims` argument. Note that
in this second call to the `plot2D` function, we have omitted the
`fcol` argument, as the `"markers"` feature variable name is the
default value. We choose to display PCs 1 and 7 to illustrate that
while upper principal components explain much less variability in the
data (2.23% for PC7, as opposed to 48.41% for PC1), we see that the
mitochondrial and peroxisome clusters can be differenciated, despite
the apparent overlap in the two first PCs.

```{r plotmarkers, fig.width = 12}
par(mfrow = c(1, 2))
plot2D(hl, fcol = "markers", main = "pRolocmarkers for mouse")
addLegend(hl, fcol = "markers", where = "bottomleft", cex = .7)
plot2D(hl, dims = c(1, 7))
```

@@

```{r}

data(hyperLOPIT2015ms3r1)
data(hyperLOPIT2015ms3r2)
data(hyperLOPIT2015ms3r3)

hyperLOPIT2015ms3r3 <- hyperLOPIT2015ms3r3[, -(2:4)]

@@

ij <- combn(3, 2)
pc <- apply(ij, 2,
            function(.ij) {
                tmp <- suppressMessages(commonFeatureNames(hll[.ij]))
                i <- intersect(tmp[[1]]$Fraction.No, tmp[[2]]$Fraction.No)
                diag(cor(t(exprs(tmp[[1]][, match(i, tmp[[1]]$Fraction.No)])),
                         t(exprs(tmp[[2]][, match(i, tmp[[2]]$Fraction.No)]))))
            })
names(pc) <- apply(ij, 2, paste, collapse = ".")
sapply(pc, summary)

data(hyperLOPIT2015ms3r3)
tmp <- commonFeatureNames(hyperLOPIT2015ms3r1[, -(2:4)],
                          hyperLOPIT2015ms3r3[, -(2:4)])
summary(diag(cor(t(exprs(tmp[[1]])), t(exprs(tmp[[2]])))))

data(hyperLOPIT2015ms3r3)
tmp <- commonFeatureNames(hyperLOPIT2015ms3r1, hyperLOPIT2015ms3r3)
summary(diag(cor(t(exprs(tmp[[1]])), t(exprs(tmp[[2]])))))
